---
title: "fars Vignette"
author: "Felix E. Rivera-Mariani, PhD"
date: "June 23, 2017"
output: html_vignette
---

The fars packages enables the analysis of datasets from the United States National Highway Traffic Safety Administration (NHTSA). The datasets are part of the NHTSA Fatal Analysis Reporting System. 

This packages is available on Github. The commands below can be used for installation.

```{r, eval=FALSE}
devtools::install_github("https://github.com/friveramariani/fars")
library(countytimezones)
```

The 3 functions below can be used for the analysis:

- fars_read()
- summarize_years()
- fars_map_state()

The "fars_read()" function reads the accidents' csv file and generate a tibble file, which can then be used to analyse the data with R functions.

```{r, eval=FALSE}
data <- fars_read(filename = "./accident_2013.csv.bz2")
```

The "summarize_years()" function generates a summary output of the accidents per year(s) for each corresponding month.

```{r, eval=FALSE}
summarize_years<-fars_summarize_years(years=2013:2015)
```

The "fars_map_state()" function enable visualizing the map location, by state and year, of accidents.

```{r, eval=FALSE}
fars_map_state(40, 2014)
```

The 2013 to 2015 accidents datasets are available in the package "inst/extdata".




